A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-13 article/02_Materials_and_Methods.Rmd
and more better figure captions

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_type.jpeg}
\caption{\label{development_burial_type}Regional distribution time series of the variable \textit{burial type} with the absolute amount (\textbf{A}) and proportion (\textbf{B}) of grave types.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_construction.jpeg}
\caption{\label{development_burial_construction}Like Figure \ref{development_burial_type}, but for the variable \textit{burial construction}.\newline\newline}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_type.jpeg}
\caption{\label{development_burial_type}Regional distribution time series of the variable \textit{burial type} with the absolute amount (\textbf{A}) and proportion (\textbf{B}) of grave types. The x-axis shows the time, the y-axis the amount or the percentage shares of graves. The individual plots are separated by region, and each region is featured by a small map according to Figure \ref{map_regions} A.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/development_burial_construction.jpeg}
\caption{\label{development_burial_construction}Like Figure \ref{development_burial_type}, but for the variable \textit{burial construction}.\newline\newline\newline\newline\newline}
\end{figure}
